\documentclass[12pt, letterpaper, preprint]{aastex63}
\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage{color}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{ctable}
\usepackage{bm}
\usepackage[normalem]{ulem} % Added by MS for \sout -> not required for final version
\usepackage{xspace}
%\usepackage{csvsimple} 

% typesetting shih
\linespread{1.08} % close to 10/13 spacing
\setlength{\parindent}{1.08\baselineskip} % Bringhurst
\setlength{\parskip}{0ex}
\let\oldbibliography\thebibliography % killin' me.
\renewcommand{\thebibliography}[1]{%
  \oldbibliography{#1}%
  \setlength{\itemsep}{0pt}%
  \setlength{\parsep}{0pt}%
  \setlength{\parskip}{0pt}%
  \setlength{\bibsep}{0ex}
  \raggedright
}
\setlength{\footnotesep}{0ex} % seriously?

% citation alias

% math shih
\newcommand{\setof}[1]{\left\{{#1}\right\}}
\newcommand{\given}{\,|\,}

\newcommand{\Om}{\Omega_{\rm m}} 
\newcommand{\Ob}{\Omega_{\rm b}} 
\newcommand{\OL}{\Omega_\Lambda}
\newcommand{\smnu}{M_\nu}
\newcommand{\sig}{\sigma_8} 
\newcommand{\mmin}{M_{\rm min}}
\newcommand{\BOk}{\widehat{B}_0} 
\newcommand{\hmpc}{\,h/\mathrm{Mpc}}
\newcommand{\bfi}[1]{\textbf{\textit{#1}}}
\newcommand{\parti}[1]{\frac{\partial #1}{\partial \theta_i}}
\newcommand{\partj}[1]{\frac{\partial #1}{\partial \theta_j}}
\newcommand{\mpc}{h/{\rm Mpc}}
\newcommand{\lgal}{{\sc LGal}}
\newcommand{\fsps}{{\sc FSPS}}
\newcommand{\tlb}{t_{\rm lookback}}
\newcommand{\zmw}{Z_{\rm MW}}
\newcommand{\tage}{t_{\rm age, MW}}
\newcommand{\tauism}{\tau_{\rm ISM}}
\newcommand{\avgsfr}{\overline{\rm SFR}_{\rm 1Gyr}}
\newcommand{\avgssfr}{\overline{\rm SSFR}_{\rm 1Gyr}}
\let\oldAA\AA
\renewcommand{\AA}{\text{\normalfont\oldAA}}
\newcommand{\github}{\href{https://github.com/changhoonhahn/provabgs/}{\faGithub}}


\makeatletter \def\@captype{figure} \makeatother

\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
% text shih
\newcommand{\etal}{\emph{et~al.}}
\newcommand{\bitem}{\begin{itemize}}
\newcommand{\eitem}{\end{itemize}}
%\newcommand{\beq}{\begin{equation}}
%\newcommand{\eeq}{\end{equation}}

%% collaborating
\newcommand{\todo}[1]{\marginpar{\color{red}TODO}{\color{red}#1}}
\definecolor{orange}{rgb}{1,0.5,0}
\newcommand{\ch}[1]{{\color{orange} #1}}

\shorttitle{PROVABGS Mock Challenge}
\shortauthors{Hahn et al.}

\begin{document} \sloppy\sloppypar\frenchspacing 

\title{The DESI PRObabilistic Value-Added Bright Galaxy Survey (PROVABGS) Mock Challenge} 
%\date{\texttt{DRAFT~---~\githash~---~\gitdate~---~NOT READY FOR DISTRIBUTION}}

\newcounter{affilcounter}
\author{ChangHoon Hahn}
\email{changhoon.hahn@princeton.edu}
\affil{Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton NJ 08544, USA} 

\author{Gyubin Kwon}
\affil{Astronomy Department, University of California at Berkeley, Berkeley, CA 94720, USA}

\author{Rita Tojeiro}
\affil{School of Physics and Astronomy, University of St Andrews, North Haugh, St Andrews, KY16 9SS, UK}

\author{Malgorzata Siudek} 
\affil{Institut de F\'{\i}sica d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, 08193 Bellaterra (Barcelona), Spain}
\affil{National Centre for Nuclear Research, ul. Pasteura 7, 02-093, Warsaw, Poland}

\author{Rebecca E. A. Canning}
\affil{}

\author{Mar Mezcua}
\affil{Institute of Space Sciences (ICE, CSIC), Campus UAB, Carrer de Can Magrans, 08193, Barcelona, Spain}
\affil{Institut d’Estudis Espacials de Catalunya (IEEC), C/ Gran Capità, 08034 Barcelona, Spain}

\author{John Moustakas}
\affil{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211, USA}

\author{Jeremy L. Tinker}
\affil{Center for Cosmology and Particle Physics, Department of Physics, New York University, New York, USA, 10003}

\author{GQP WG}

\begin{abstract}
    The PRObabilistic Value-Added Bright Galaxy Survey (PROVABGS) will provide
    measurements of galaxy properties, such as stellar mass ($M_*$), star
    formation rate (SFR), stellar metallicity ($Z_{\rm MW}$), and stellar age
    ($t_{\rm age, MW}$), for ${>}10$ million galaxies of the DESI Bright Galaxy
    Survey.
    Full posterior distributions of the galaxy properties will be inferred
    using state-of-the-art Bayesian spectral energy distribution (SED) modeling
    of DESI spectroscopy and Legacy Surveys photometry.
    In this work, we present the SED model, Bayesian inference framework, and
    methodology of PROVABGS. %\footnote{publicly available at }.
    Furthermore, we construct realistic synthetic DESI spectra and photometry
    using galaxies in the {\sc L-Galaxies} semi-analytic model
    %, based on their star formation and chemical enrichment histories, 
    and apply the PROVABGS SED modeling on the mock observations.
    We then compare the galaxy properties that we infer to the true galaxy
    properties of the simulation using a hierarchical Bayesian framework
    to quantify accuracy and precision. 
    Overall, we accurately infer the true $M_*$, SFR, $Z_{\rm MW}$, and 
    $t_{\rm age, MW}$ of the simulated galaxies. 
    However, we find that priors on galaxy properties induced by the SED model
    have a significant impact on the posteriors. 
    We characterize the priors and their impact in detail: they impose a 
    ${\rm SFR}{>}10^{-1} M_\odot/{\rm yr}$ lower bound on SFR, a ${\sim}0.3$
    dex bias on $\log Z_{\rm MW}$ for galaxies with low spectral
    signal-to-noise, and $t_{\rm age, MW} < 8\,{\rm Gyr}$ upper bound on
    stellar age. 
    We also demonstrate that a joint analysis of spectra and photometry
    significantly improves the constraints on galaxy properties over photometry
    alone and is necessary to mitigate the impact of the priors. 
    With the methodology presented and validated in this work, PROVABGS will
    maximize information extracted from DESI observations and provide a galaxy
    catalog that will extend current galaxy studies to new regimes and unlock 
    cutting-edge probabilistic analyses. \github
\end{abstract}

\keywords{
    cosmology: observations -- galaxies: evolution -- galaxies: statistics 
}

% --- intro ---  
\input{intro}
% --- sims ---  
\input{sims} 
% --- methods ---  
\input{methods}
% --- results ---  
\input{results}
% --- discussion ---  
\input{discuss}
% --- summary ---  
\input{summary}

\section*{Acknowledgements}
It's a pleasure to thank
    Justin Alsing, 
    Adam Carnall, 
    Kartheik Iyer, 
    Joel Leja, 
    Jenny Greene, 
    and 
    Peter Melchior
for valuable discussions and comments. 
This material is based upon work supported by the U.S. Department of Energy,
Office of Science, Office of High Energy Physics, under contract No.
DE-AC02-05CH11231.  This project used resources of the National Energy Research
Scientific Computing Center, a DOE Office of Science User Facility supported by
the Office of Science of the U.S.  Department of Energy under Contract No.
DE-AC02-05CH11231. 
CH is supported by the AI Accelerator program of the Schmidt Futures Foundation.
MS is supported by the European Union's  Horizon 2020 research and innovation
programme under the Maria Sk\l{}odowska-Curie (grant agreement No 754510), the
National Science Centre of Poland (grant UMO-2016/23/N/ST9/02963) and by the
Spanish Ministry of Science and Innovation through Juan de la Cierva-formacion
program (reference FJC2018-038792-I).
MM acknowledges support from the Ramon y Cajal fellowship (RYC2019-027670-I).

This research is supported by the Director, Office of Science, Office of High
Energy Physics of the U.S. Department of Energy under Contract No.
DE–AC02–05CH11231, and by the National Energy Research Scientific Computing
Center, a DOE Office of Science User Facility under the same contract;
additional support for DESI is provided by the U.S. National Science
Foundation, Division of Astronomical Sciences under Contract No. AST-0950945 to
the NSF’s National Optical-Infrared Astronomy Research Laboratory; the Science
and Technologies Facilities Council of the United Kingdom; the Gordon and Betty
Moore Foundation; the Heising-Simons Foundation; the French Alternative
Energies and Atomic Energy Commission (CEA); the National Council of Science
and Technology of Mexico; the Ministry of Economy of Spain, and by the DESI
Member Institutions.

The authors are honored to be permitted to conduct scientific research on
Iolkam Du’ag (Kitt Peak), a mountain with particular significance to the Tohono
O’odham Nation.


\appendix
\input{nmf}
\input{modelprior}
\input{hyper}

\bibliographystyle{mnras}
\bibliography{gqp_mc} 
\end{document}
